### 2024-03-20 sections/1stratified.tex
Changed to Emb and some work in \S 4.

\begin{definition}
    $\mfld$ is the $\infty$-category whose objects are stratified manifolds and whose morphisms are open embeddings among them. It is presented as the $\mathsf{Kan}$-enriched category of stratified manifolds by taking the Kan complex of morphisms between two objects $M$ and $N$ to be defined by
    %
    \begin{equation}
        \mathsf{Hom}_{\mfld} (M, N): [p] \mapsto \mathsf{Mfld}_{/\Delta^p} (M \times \Delta^p, N \times \Delta^p).
    \end{equation}
    %
    Here, $\mathsf{Mfld}_{/\Delta^p}$ takes the morphism set in the over-category over $\Delta^p$.
\end{definition}

>>>>

\begin{definition}\label{def:mfld_infty_cat}
    $\mfld$ is the $\infty$-category whose objects are stratified manifolds and whose morphisms are open embeddings among them. It is presented as the $\mathsf{Kan}$-enriched category of stratified manifolds by taking the Kan complex of morphisms between two objects $M$ and $N$ to be defined by
    %
    \begin{equation}
        \mathsf{Hom}_{\mfld} (M, N): [p] \mapsto \mathsf{Emb}_{\Delta^p} (M \times \Delta^p, N \times \Delta^p),
    \end{equation}
    %
    where $\mathsf{Emb}_{\Delta^p} (M \times \Delta^p, N \times \Delta^p)$ denotes the embeddings from $M \times \Delta^p$ to $N \times \Delta^p$ that commute on the nose with the projections to $\Delta^p$.
\end{definition}
